Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
our->several in 5th idea of pf

\sssec*{Idea of Proof:}
The method of this proof is almost identical to that of Theorem
~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points,
and then increment the stabilizer orders of stacky points, checking
that the theorem holds at each step. The more technical case occurs
when $\delta = 0$, in which case we simply increment the stabilizer
orders of stacky points starting from one of our base cases, and
check that every stacky curve can be reached by a sequence of
admissible incrementations from a base case.

>>>>

\sssec*{Idea of Proof:}
The method of this proof is almost identical to that of Theorem
~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points,
and then increment the stabilizer orders of stacky points, checking
that the theorem holds at each step. The more technical case occurs
when $\delta = 0$, in which case we simply increment the stabilizer
orders of stacky points starting from one of several base cases, and
check that every stacky curve can be reached by a sequence of
admissible incrementations from a base case.
